---
title: "Untitled"
output: html_document
date: "2025-04-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
만약 $l = 4$일 때
귀무가설
\begin{equation*}
  H_0 : \alpha_1 = 2 \alpha_2 = 3 \alpha_3
\end{equation*}
을 검정하는 검정통계량 $F_0$를 구하시오.

조건은 다음과 같다.

$\displaystyle\sum_{i=1}^{l}\alpha_i = 0,~~  \displaystyle\sum_{j=1}^{m}\beta_j = 0, ~~ l =4$

추가적인 힌트 :

1. $C$의 형태, $\boldsymbol{\mathbf{\beta}} = (\mu, \alpha_1, \alpha_2, \alpha_3, \alpha_4, \beta_1, \cdots, \beta_m)^{\top}$의 형태

\begin{equation*}
  C =
  \begin{pmatrix}
    0 & 1 & -2 & 0 & 0 & 0 & \cdots & 0 \\
    0 & 0 & 2 & -3 & 0 & 0 & \cdots & 0
  \end{pmatrix},
\end{equation*}

2. $F_0 = \cfrac{Q/2}{S_E/((l-1)(m-1))} \sim F(2, (l-1)(m-1))$에서 Q의 형태

\begin{equation*}
  Q = (C\hat{\boldsymbol{\mathbf{\beta}}})^{\top}[C(X^{\top}X)^{-1}C^{\top}]^{-1}(C\hat{\boldsymbol{\mathbf{\beta}}})
\end{equation*}

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
